%!TEX program = xelatex

\documentclass[11pt]{article}

%%%------------------------------------------------------------------------
%%% Metadata
%%%------------------------------------------------------------------------

\def\myauthor{Joseph Vincent Casillas}
\def\mytitle{Vita}
\def\mycopyright{\myauthor}
\def\mykeywords{}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
\def\myaffiliation{University of Arizona}
\def\myaddress{Department of Spanish and Portuguese}
\def\myemail{jvcasill@email.arizona.edu}
\def\myweb{http://www.jvcasillas.com}
\def\myphone{(520) 621-4702}
\def\myfax{(520) 621-6104}
\def\myversion{1.0}
\def\myrevision{.1}


\def\myaffiliation{University of Arizona}
\def\myauthor{Joseph Vincent Casillas}
\date{} % not used (revision control instead)
\def\mykeywords{Casillas, Joseph, Joseph Casillas, Vita, CV, Resume, Linguistics}


%%%------------------------------------------------------------------------
%%% Required style files
%%%------------------------------------------------------------------------
\usepackage{url,fancyhdr}

%% needed for xelatex to work
\usepackage{fontspec}
\usepackage{xunicode}

%% color for the links 
\usepackage[usenames,dvipsnames]{color}



%% hyperlinks
\usepackage[xetex, 
	colorlinks=true,
	urlcolor=BlueViolet,
	plainpages=false,
  	pdfpagelabels,
  	bookmarksnumbered,
  	pdftitle={\mytitle},
  	% pagebackref,
  	pdfauthor={\myauthor},
  	pdfkeywords={\mykeywords}
  	]{hyperref}


%% my stuff
\let\sups\relax
\usepackage{tipa}
\usepackage{geometry}
\usepackage{multicol}
\usepackage[spanish, english]{babel}
\usepackage{natbib}
\usepackage{bibentry}
\newcommand{\bibverse}[1]{\begin{verse} \bibentry{#1}. \end{verse}}

\geometry{
  body={390pt, 592pt},
  left=115.63pt,
  top=1.1in,
  bottom=1.1in
}

\pagestyle{myheadings}
\markright{\myauthor}
\thispagestyle{empty}

\AtBeginDocument{
  \renewcommand\textipa[2][r]{{\fontfamily{cm#1}\tipaencoding #2}}
}

\renewenvironment{IPA}[1][r]
 {\fontfamily{cm#1}\tipaencoding}
 {}
%%%------------------------------------------------------------------------
%%% Document
%%%------------------------------------------------------------------------
\begin{document}

%% Choose fonts for use with xelatex
%% Minion and Myriad are widely available, from Adobe. 
%% Pragmata is available to buy at http://www.fsd.it/fonts/pragma.htm
%% and is worth every penny. Any good monospace font will work fine, though.
%% Consolas or inconsolata are good alternatives.
\setromanfont[Mapping={tex-text},Numbers={OldStyle},Ligatures={Common}]{Minion Pro} 
\setsansfont[Mapping=tex-text,Colour=AA0000]{Myriad Pro}
\setmonofont[Mapping=tex-text,Scale=0.9]{Consolas} 



%%%------------------------------------------------------------------------
%%% Local commands
%%%------------------------------------------------------------------------

%% Marginal header
%% Note: as the document goes on you may need to introduce a (gradually increasing)
%% \vspace element to keep the marginal header pleasingly aligned with the first 
%% item in the body text. Like this: \marginhead{{\vskip 0.4em}Grants}, or 
%% \marginhead{{\vskip 0.8em}Service}. Experiment as needed.
\newcommand{\marginhead}[1]{\marginpar{\textsf{{\footnotesize\vspace{-1em}\flushright #1}}}}


%% custom ampersand (font consistent with the one chosen above)
\newcommand{\amper}{{\fontspec[Scale=.95,Colour=AA0000]{Minion Pro Medium}\selectfont\&\,}}

%% No bullets on labels
\renewcommand{\labelitemi}{~} 

%% Custom hanging indent for vita items
\def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
%\def\ind{\hangindent=18pt\hangafter=1 \noindent}
\def\labelitemi{~}
\renewcommand{\labelitemii}{~}

%%%------------------------------------------------------------------------
%%% Page layout
%%%------------------------------------------------------------------------
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhead{}
\fancyfoot{}
\rhead{{\scriptsize\thepage}}
\lhead{{\scriptsize{\sc \myauthor}}}

%% git revision control footer 
% \rfoot{\texttt{\scriptsize \VCRevision\ on \VCDateTEX}} % git revision info inserted via external script -- see docs for vc package for details. comment out this line if you're not using vc, and also remove the \input{vc} line above.

%%%------------------------------------------------------------------------
%%% Address and contact block
%%%------------------------------------------------------------------------
\begin{minipage}[t]{3.3in}
 \flushright {\footnotesize \href{http://www.arizona.edu}{University of Arizona} \\ Department of Spanish and Portuguese \\ Modern Languages \\ \vspace{-0.05in} Tucson, \textsc{az} 85721}  
  
\end{minipage}
\hfill     
%\begin{minipage}[t]{0.0in}
% dummy (needed here)
%\end{minipage}
\hfill
\begin{minipage}[t]{1.7in}
  \flushright \footnotesize Phone: \myphone \\ 
  Fax: \myfax  \\ 
  {\scriptsize \texttt{\href{mailto:\myemail}{\myemail}}} \\
  {\scriptsize \texttt{\href{\myweb}{\myweb}}}
\end{minipage}


\bigskip

%% Name 
\vspace{.1in}\noindent{\Large {\textsc{Joseph Vincent Casillas}}}
\reversemarginpar

\bigskip       



%% Education

\marginhead{{\vskip -0.3em}Education}
\noindent Ph.D, Hispanic Linguistics, University of Arizona, in progress. \vspace{-0.1in}
\begin{itemize}
  \item \small Minor: Second Language Acquisiton and Teaching.
\end{itemize} 

\noindent M.A., Hispanic Linguisctics, University of Arizona, 2012. \vspace{-0.1in}
\begin{itemize}
  \item \small Thesis: \emph{Production, perception and processing of English-specific \\vowel contrast by early Spanish-English bilinguals}.
\end{itemize} 

\noindent M.A., Spanish Philology, Middlebury College, 2009. \\ \vspace{-0.1in}

\noindent B.A., \hspace{.4mm} Psychology, Western Washington University, 2006. \\ \vspace{-0.1in}

\noindent B.A., \hspace{.4mm} Spanish, Western Washington University, 2006. 


\bigskip
 

%% Teaching experience
\marginhead{{\vskip 0.3em}Teaching \mbox{experience}}
\medskip
\noindent Graduate Associate in Teaching, University of Arizona, 2012--present. \\ \vspace{-0.1in}

\noindent Graduate Assistant in Teaching, University of Arizona, 2010--2012. \\
\noindent Courses taught (in Spanish unless otherwise noted):\vspace{-0.075in}
\begin{itemize}
  \item \small \emph{Spanish 102 (2nd semester Spanish)}.\vspace{-0.1in}
  \item \small \emph{Spanish 251 (5th semester Spanish)}.\vspace{-0.1in}
  \item \small \emph{Spanish 340: Introduction to Spanish Phonetics}.\vspace{-0.1in}
  \item \small \emph{Spanish 343: Spanish Phonetics for the Heritage Speaker}.\vspace{-0.1in}
  \item \small \emph{Spanish 452: Introduction to Hispanic Linguistics}.\vspace{-0.1in}
  \item \small \emph{Spanish 455: History of the Spanish Language}.\vspace{-0.1in}
  \item \small \emph{Spanish 457: Applied Linguistics}.
\end{itemize} 
\noindent English Teacher, C.E.I.P Carmen Iglesias, Madrid, Spain, 2009--2010 \\ \vspace{-0.1in}

\noindent Teaching Assistant, Escuela Oficial de Idiomas, Cádiz, Spain, 2006--2008.


\bigskip
 

%% Research experience
\marginhead{{\vskip 0.4em}Research \mbox{experience}}
\medskip
\noindent Research assistant, Arizona Applied Phonetics Laboratory, 2011--Present. \\ 
University of Arizona, Lab director: Dr. Miquel Simonet. \\ \vspace{-0.1in}

\noindent Research assistant, Spanish Heritage Language Program, Spring 2012. \\ 
University of Arizona, Director: Dr. Sara Beaudrie. \\ \vspace{-0.1in}

\noindent Assistant to the Director, Spanish Heritage Language Program, Fall 2011. \\
University of Arizona, Director: Dr. Sara Beaudrie. \\ \vspace{-0.1in}

\noindent Phonetics lab assistant, Center of Social and Human Sciencies, Madrid, Spain, 2010. \\ 
Spanish High Council of Scientific Investigation (CSIC), Lab director: María Juana Gil Fernández.


% \bigskip
\clearpage

% Professional development
\marginhead{{\vskip 0.6em}Professional \mbox{development}}
\medskip
\noindent Research and Instructional Computing Workshop and Open Hour Assistant, 2013--Present. \\
College of Humanities, University of Arizona, Tucson, AZ. \\ \vspace{-0.1in}

\noindent Bilingual Assistant, Middlebury College, Middlebury, VT, Summer 2013. \\
Pronunciation Clinic (co-teaching undergraduate workshop), Assistant to Dr. Armin Schwegler. \\ \vspace{-0.1in}

\noindent Bilingual Assistant, Middlebury College, Middlebury, VT, Summer 2012. \\
Introduction to Spanish Phonetics (graduate course), Pronunciation Clinic (undergraduate workshop), Assistant to Dr. Luis Ortiz López. \\ \vspace{-0.1in}

\noindent Diploma of Spanish as a Foreign Language (DELE), Instituto Cervantes, Spain, 2008. \\ 
Level Superior (C2) in accordance with the Common European Framework of Reference for Languages (CEFR). \\ \vspace{-0.1in}

\noindent Representative for Foreign Language Associates Northwest (FLAN), Washington Association of Foreign Language Teachers regional conference, 2006. \\ \vspace{-0.1in}

\noindent Certificate of Hispanic Studies, University of Granada, Granada, Spain, 2004. 


\bigskip


% Grants and scholarships
\marginhead{{\vskip 0.4em}\mbox{Grants and} scholarships}
\medskip
\noindent Comanche Nation Department of Higher Education Scholarship, 2008--2014. \\ \vspace{-0.1in} 

\noindent College of Humanities Fellowship, University of Arizona, 2013. \\ \vspace{-0.1in}

\noindent Second Language Acquisition and Teaching Travel Grant, University of Arizona, 2013. \\
Awarded for travel to the Second Language Research Forum (SLRF). \\ \vspace{-0.1in} 

\noindent College of Humanities Fellowship, University of Arizona, 2010--2011. \\ \vspace{-0.1in}

\noindent Graduate College Fellowship, University of Arizona, 2010--2011.\\ \vspace{-0.1in}

\noindent North American Language and Culture Scholarship, Spanish Ministry of Education and Science, 2006--2008. \\ \vspace{-0.1in}

\noindent Eunice D. Faber Scholarship, Western Washington University, 2004--2006.


\bigskip


\marginhead{{\vskip 0.3em}Academic \mbox{honors}}
\medskip
\noindent Outstanding Graduate Student, Middlebury College, 2009. \\ \vspace{-0.1in}

\noindent Outstanding Graduating Senior Nominee, Department of Psychology, Western Washington University, 2006. \\ \vspace{-0.1in}

\noindent Outstanding Graduating Senior Nominee, Department of Modern and Classical Languages, Western Washington University, 2006.


\bigskip


\marginhead{{\vskip -0.3em}Publications}
\nobibliography*

\noindent Articles \\ \vspace{-0.1in}

\noindent \bibentry{Casillas2012}. \\ \vspace{-0.1in}

\noindent \bibentry{Casillas2010}. \\ \vspace{-0.1in}

\noindent \bibentry{Casillas2009}. \\ 


\medskip


\noindent Proceedings \\ \vspace{-0.1in}

\noindent \bibentry{CasillasWSS62013}. \\


\medskip


\marginhead{{\vskip -0.1em}Presentations}
\noindent Oral Presentations \\ \vspace{-0.1in}

\noindent \bibentry{CasillasSLRF2013}. \\ \vspace{-0.1in}

\noindent \bibentry{CasillasPAPI2013}. \\ \vspace{-0.1in}

\noindent \bibentry{CasillasWSS62013}. \\ \vspace{-0.1in}

\noindent \bibentry{CasillasCONF2012a}. \\ \vspace{-0.1in}

\noindent \bibentry{CasillasCONF2011}. \\ \vspace{-0.1in}

\noindent \bibentry{CasillasCONF2011a}. \\ 


\medskip


\ind Poster Presentations \\ \vspace{-0.1in}

\noindent \bibentry{CasillasPPLC2013}.
 

\bigskip 
% \clearpage


\marginhead{{\vskip 0.3em}\mbox{Service and} outreach}
\medskip
\noindent Co-technology Director, Department of Spanish and Portuguese Film Festival, 2011--2014. \\ \vspace{-0.1in}

\noindent Chair, Perception and Production of Phonological Variables. 6th International Workshop on Spanish Sociolinguistics, University of Arizona, Tucson, AZ, 2012. \\ \vspace{-0.1in}

\noindent Organizing Committee, 6th International Workshop on Spanish Sociolinguistics, University of Arizona, Tucson, AZ, 2011--2012.  \\ \vspace{-0.1in}

\noindent Assistant Editor, Arizona Journal of Hispanic Cultural Studies, Vol. 15, 2011. \\ \vspace{-0.1in}

\noindent Webmaster, Divergencias: Revista de estudios lingüísticos y literarios, 2011--2012. \\ \vspace{-0.1in}

\noindent Editor, Divergencias: Revista de estudios lingüísticos y literarios, Vol. 10, 1, 2012. \\ \vspace{-0.1in}

\noindent Technology Director, University of Arizona Spanish and Portuguese Graduate Symposium, 2010--2012. \\ \vspace{-0.1in}

\noindent Editor, Divergencias: Revista de estudios lingüísticos y literarios, Vol. 8, 2, 2010. \\ \vspace{-0.1in}

\noindent Assistant Editor, Arizona Journal of Hispanic Cultural Studies, Vol. 14, 2010.


\bigskip 


\marginhead{{\vskip -0.3em}Professional memberships}
\noindent Modern Language Association \\ \vspace{-0.1in}

\noindent Sigma Delta Pi National Hispanic Honor Society, Chapter MU \\ \vspace{-0.1in}

\noindent The American Council on the Teaching of Foreign Languages \\ \vspace{-0.1in}

\noindent Psi Chi International Honors Society in Psychology, Western Washington University


\bigskip 

 
\marginhead{{\vskip -0.3em}Additional interests}
\noindent Languages \vspace{-0.1in}
\begin{itemize}
  \item English \vspace{-0.1in}
  \item Spanish \vspace{-0.1in}
  \item French
\end{itemize}

\noindent Programing Languages \vspace{-0.1in}
\begin{itemize}
  \item R \vspace{-0.1in}
  \item Python \vspace{-0.1in}
  \item HTML \vspace{-0.1in}
  \item Lisp \vspace{-0.1in}
  \item TeX \vspace{-0.1in}
  \item Markdown
\end{itemize}

\noindent Technology \vspace{-0.1in}

\begin{multicols}{3}
  \begin{itemize}
  \item Mac OS X \vspace{-0.1in}
  \item Windows \vspace{-0.1in}
  \item Linux \vspace{-0.1in}
  \item Adobe Creative Suite

  \item SPSS \vspace{-0.1in}
  \item R \vspace{-0.1in}
  \item Goldvarb X \vspace{-0.1in}
  \item Praat 

  \item PsychoPy \vspace{-0.1in}
  \item SuperLab 4.5 \vspace{-0.1in}
  \item Emacs \vspace{-0.1in}
  \item \LaTeX
  \end{itemize}
\end{multicols}

\vspace{-0.1in}

\noindent \rule{390pt}{.5 mm}

\smallskip

\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{http://www.jvcasillas.com}{http://www.jvcasillas.com}
  \end{footnotesize}
\end{center}

\bibliographystyle{apalike}
\nobibliography{publicationsCV}
\end{document}